\section{Experimental protocol}

\paragraph{Models.}
We evaluate \texttt{gpt-4.1-nano}, \texttt{gpt-4.1-mini}, and
\texttt{gpt-4.1}, all accessed through the API with temperature 0 and a maximum
of 256 output tokens. The paper-facing experiments were run on June 28, 2026.
Because OpenAI's current model documentation lists GPT-5.5 as the flagship model
and GPT-5.4 mini/nano as lower-cost variants \citep{openai2026models}, our
model coverage should be read as a GPT-4.1-family pilot rather than a claim
about the newest available model family.

\paragraph{Prompting conditions.}
Each model is run under two system-prompt conditions. The baseline prompt is
``You are a helpful assistant.'' The mitigation condition uses a \textbf{Global
Interaction Contract} prompt that instructs the model to infer instruction and
content language separately, preserve content language during editing unless
translation is requested, preserve quoted spans and literal data, obey explicit
script/register/locale constraints, and avoid unnecessary explanatory framing.

\paragraph{Repairs.}
For each failed first response, we append the item's first standardized repair
prompt and rescore the next response. If the response still fails, we append a
second standardized repair. The trajectory stops at first success or after two
repairs. This fixed repair budget lets us compare models and prompts under the
same user burden. It also separates first-turn usability from recoverability:
some models fail initially but repair quickly, while others continue to violate
literal-preservation constraints.

\paragraph{Scoring.}
Automatic scoring combines deterministic checks for exact span preservation and
script with rule-based language and task checks. The scorer emits both a binary
FTGA label and component labels for language, script, preservation, task, and
register/locale. We run scorer-ablation diagnostics by relaxing one component
at a time, and deterministic regression tests cover controlled language, script,
preservation, task, and register/locale failures.

\paragraph{Audit.}
We run a blinded \texttt{gpt-4.1} judge audit on 72 first-turn responses,
sampling three responses from each model-condition-family stratum. The judge
sees the user prompt, expected contract, and assistant response, but not model
identity or prompting condition. This is a scorer sanity check, not a native- or
near-native human validation study.
